---
title: "Bivariate stat"
author: "Norman Poh"
date: "3 October 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Init
```{r}
setwd("L:/loading")

library(palab)
library(palabmod)
library(ggplot2)
library(tidyverse)
library(stringr)
library(lubridate)
library(tictoc)
library(hashmap)
library(ROCR)
source("../lib/cut_linux.R")
source("../lib/mystat.R")
source('../lib/plot_cond_density.R')

```

```{r}
combined = readRDS("D:/Data/Processed/combined_date_data.rds")
config = readRDS("D:/Data/Processed/combined_date_config_validated.rds")
#write_csv(combined_date_data,"D:/Data/Processed/combined_date_data.csv")
#write_csv(combined_date_config,"D:/Data/Processed/combined_date_config_validated.csv")

var_config_generator(input_csv = "D:/Data/Processed/combined_date_data.csv",
                     prefix = "final_",
                     output_dir = "D:/Data/Processed")
#var_config output is D:/Data/Processed/final_var_config.csv
```

## Checking

```{r}
final_config = read_csv("D:/Data/Processed/final_var_config.csv")
config = read_csv("D:/Data/Processed/combined_date_config_validated.csv")

sum(final_config$Column==config$Column)
length(config$Column)

#final_config$Type = config$Type
final_config$Type[ final_config$Column=='pat_id' ] = 'key'
final_config$Type[ config$isdate ] = 'others'
final_config$Type[ final_config$Column=='npi'] = 'others'

#final_config$Column[str_detect(colnames(combined),'flg')]
final_config$Type[ str_detect(colnames(combined),'flg')] = 'categorical'
final_config$Description = config$Description

write_csv(final_config, "D:/Data/Processed/final_var_config.csv")
```
## Univariate stats

```{r}
univar_results <- univariate_stats(input = combined,
  var_config = "D:/Data/Processed/final_var_config.csv",
  output_dir = "D:/Data/QC/univar",
  vargt0 = FALSE)

View(univar_results$cat)

```
## remove variables that are poorly populated
Variable	Problem
pre_concom_gpif_fst8	Variable is 100% missing
pre_concom_gpif_lst8	Variable is 100% missing
pre_medication_fst11	Variable is 100% missing
pre_medication_lst11	Variable is 100% missing
pre_medication_fst13	Variable is 100% missing
pre_medication_lst13	Variable is 100% missing
pre_concom_gpif_fst8_diff	Variable is 100% missing
pre_concom_gpif_lst8_diff	Variable is 100% missing
pre_medication_fst11_diff	Variable is 100% missing
pre_medication_lst11_diff	Variable is 100% missing
pre_medication_fst13_diff	Variable is 100% missing
pre_medication_lst13_diff	Variable is 100% missing
pre_script_fst_diff	Variable is 100% missing
pre_script_lst_dayssup_diff	Variable is 100% missing
post_script_lst_dayssup_diff	Variable is 100% missing
pre_concom_gpif_num8	Variable has only 1 unique value
pre_medication_num11	Variable has only 1 unique value
pre_medication_num13	Variable has only 1 unique value
pre_concom_ndc_fst4_diff	Variable has only 1 unique value
pre_concom_ndc_lst4_diff	Variable has only 1 unique value

```{r}
var2remove = c('pre_concom_gpif_fst8','pre_concom_gpif_lst8','pre_medication_fst11','pre_medication_lst11','pre_medication_fst13','pre_medication_lst13','pre_concom_gpif_fst8_diff','pre_concom_gpif_lst8_diff','pre_medication_fst11_diff','pre_medication_lst11_diff','pre_medication_fst13_diff','pre_medication_lst13_diff','pre_script_fst_diff','pre_script_lst_dayssup_diff','post_script_lst_dayssup_diff','pre_concom_gpif_num8','pre_medication_num11','pre_medication_num13','pre_concom_ndc_fst4_diff','pre_concom_ndc_lst4_diff')

length(var2remove)

#remove the variables from data and from the config file
final_config = final_config %>% filter( ! (final_config$Column %in% var2remove) )

config = config %>% filter( ! (config$Column %in% var2remove) )


#make correction
final_config$Type[ str_detect(final_config$Column,'_diff$') ] = 'numerical'

combined = combined %>% select( -matches(paste(var2remove, collapse="|"))) 

# Check for consistency
nrow(final_config) 
ncol(combined)
sum(colnames(combined) == final_config$Column)

# we save the var_config for QC use
write_csv(final_config, "D:/Data/QC/var_config.csv")
```

## when the outcome is discrete
```{r}
bivariate_stats_cat(input = combined, 
                    var_config = "D:/Data/QC/var_config.csv",
                    outcome_var = "discontinue_flg", 
                    output_dir = "D:/Data/QC/bivar_stats_cat",
                    count = 5, 
                    vargt0 = FALSE)
```

## plot all numerical values except those containing flg

```{r}
#debug(plot_cond_density)
#undebug(plot_cond_density)

library(R.utils)

#final_config$Description == config$Description

dim(final_config)
dim(combined)

colnames_ = colnames(combined)

# selected_var = (final_config$Type=="numerical" |
#   final_config$var_type == "date-difference" ) & 
#   ! str_detect(final_config$Column, "NPI|age_group|HCE_ID")

selected_var = final_config$Type=="numerical" &
   ! str_detect(final_config$Column, "npi|age_group|hce_id")
        
indices = which(selected_var)
colnames_[indices]

count_stat = vector(mode = "list", length = length(indices))

mkdirs("D:/Data/QC/univar_cond")
for (j in 1:length(indices)) {
  var_index = indices[j]
  print( sprintf("%s", colnames_[var_index]))
  desc_ = final_config$Description[var_index]
  #print( quantile( as.matrix(combined_data[,indices[j]]), na.rm = TRUE) ) 
  count_stat[[j]] = plot_cond_density(combined, 
    var_index = indices[j], 
    target = combined$discontinue_flg,
    target_label = 'discon',
    description = desc_,
    alpha_cut_off = 0.95, rm.zero = TRUE)
  eer_ = count_stat[[j]]$eer
  fname = sprintf( "D:/Data/QC/univar_cond/main_biogen_explore_combined_data_datediff__cond_density__%s.png",colnames_[indices[j]] )

  ggsave(fname, plot = last_plot())
  
}

eer_ = as.numeric(as.data.frame( lapply(count_stat, function(x) {(x$eer)})) )
pos_ = as.numeric(as.data.frame( lapply(count_stat, function(x) {(x$pos)})) )
neg_ = as.numeric(as.data.frame( lapply(count_stat, function(x) {(x$neg)})) )

eer_table = tibble(Column = colnames_[indices], eer = eer_,`# pos` = pos_, `# neg` = neg_)
write_csv(eer_table, 'D:/Data/QC/num_eer_analysis.csv')

```

## Bivariate stat for numerical variables

```{r}
config_ = final_config %>% filter( Type=="numerical" 
                             | Type =="key" | Column =="discontinue_flg")

write_csv(config_, "D:/Data/QC/var_config_numeric.csv")


data_ = combined %>%   select(matches(paste(config_$Column, collapse="|")))

bivar_stats_y_flag(input = data_, #as.data.frame(numeric(data__)), 
  var_config = "D:/Data/QC/var_config_numeric.csv",
  outcome_var = "discontinue_flg",
  output_dir = "D:/Data/QC/bivar_stats_num")
```

## Further filter out variables
```{r}
eer_table = read_csv('D:/Data/QC/num_eer_analysis.csv')

windows2unix_path <- function (windows_path) {
  return(str_replace(windows_path,'\\','/'))
}
  
table_ = eer_table %>% filter( eer <=0.04 )
write_csv(table_,'D:/Data/QC/var_removed_due_to_low_eer.csv')

View(eer_table)
table_ = eer_table %>% filter( eer >0.04 )

table__ = table_ %>% filter( `# pos`<=5 )
write_csv(table__,'D:/Data/QC/var_removed_due_to_npos_ls_05.csv')

table__ = eer_table %>% filter( eer >0.04 ) %>% filter( `# pos` > 5 & `# pos`<=10 )
write_csv(table__,'D:/Data/QC/var_removed_due_to_npos_ls_10.csv')

```

## remaining variables
```{r}

table.remaining = eer_table %>% filter( eer >0.04 ) %>% filter( `# pos`>10 ) 
write_csv(table.remaining,'D:/Data/QC/var_remained.csv')

```