---
title: "Modelling"
author: "Norman Poh"
date: "4 October 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
setwd("C:/Users/npoh/Documents/Git/projects/Biogen_Tecf2017_round5/modelling")
library(palab)
library(palabmod)
library(ggplot2)
library(tidyverse)
library(stringr)
library(lubridate)
library(tictoc)
library(hashmap)
library(xgboost)
library(R.utils)
source("../lib/cut_linux.R")
source("../lib/mystat.R")
source('../lib/plot_cond_density.R')
source('../lib/remove_na.R')
```

```{r}
results_dir = "D:/Results/xgb_model_full_no_diff/"
mkdirs(results_dir)
```

## Variable inclusion/exclusion criteria
```{r}
config = read_csv("D:/Data/Processed/combined_date_config_validated.csv")
combined = readRDS("D:/Data/Processed/combined_date_data.rds")
```

## Derive new variables last-minute
```{r}
combined$effective_year_diff =  (mdy(combined$effective_year) - mdy(combined$idx_dt))/365.25

numUniqueValues = length(unique((combined$effective_year_diff)))

new_row = tibble(Column = 'effective_year_diff',
                 Type = 'numerical',
                 NumUniqueValues = numUniqueValues,
                 Description = 'Effecitve years of service',
                 isdate = FALSE,
                 var_grouping = "Physician Characteritics",
                 var_period = NA)

config = rbind(config, new_row)

dim(config)
dim(combined)
       
```

##  Eliminating variables
```{r}
eer_table = read_csv('D:/Data/QC/num_eer_analysis.csv')

# eliminate var that is empty
var2remove = c('pre_concom_gpif_fst8','pre_concom_gpif_lst8','pre_medication_fst11','pre_medication_lst11','pre_medication_fst13','pre_medication_lst13','pre_concom_gpif_fst8_diff','pre_concom_gpif_lst8_diff','pre_medication_fst11_diff','pre_medication_lst11_diff','pre_medication_fst13_diff','pre_medication_lst13_diff','pre_script_fst_diff','pre_script_lst_dayssup_diff','post_script_lst_dayssup_diff','pre_concom_gpif_num8','pre_medication_num11','pre_medication_num13','pre_concom_ndc_fst4_diff','pre_concom_ndc_lst4_diff')


# eliminate variables based on others type
config$Type[config$Column=='npi'] = 'others'
config$Type[config$Column=='pat_id'] = 'key'
config$Type[config$Column=='yob'] = 'others'
config$Type[config$Column=='yomsg'] = 'others'
config$Type[config$Column=='first_tec_rx'] = 'others'
config$Type[config$Column=='effective_year'] = 'others'

config$var_grouping[ config$Column=='pat_id'] = 'id' # added this in as the var_grouping info is wrong!

var_others = config$Column[config$Type=='others']

length(var_others)
# EER and number of positivie criteria
table.eliminate = eer_table %>% filter( (eer <0.04 |  `# pos`<=10 ) )

# should get 123
length(unique(  c(table.eliminate$Column, var2remove)))

var2eliminate = unique(  c(table.eliminate$Column, var2remove, var_others) )

length(var2eliminate)  

config_ = config %>% filter( !(Column %in% var2eliminate  )) 
combined_ = combined %>% select( -one_of(var2eliminate))

length(config$Column)  
length(config_$Column) 

dim(combined_)
dim(config_) 
```
## Summary

I have worked out a list of variables to be eliminated on the basis of:
1.	100% missing
2.	Having only 1 unique value when it is a numerical variable 
3.	Having no value for the positive class
4.	Perfect separation on the basis of zero equal error rate; which indicates them being self-predictors. Three variables are: follow_up_end_dt_diff, disc_dt_diff, tot_dayssup_180)
5.	Very low equal error rate but nonzero, again, due to being a self-predictor, e.g., the total number of tecfidera fills (sum_fill)
6.	Having no more than 5 observed measurements for the positive class
7.	Having no more than 10 observed measurements for the positive class

In total, 123 variables are eliminated and so we have 324 usable variables in the end.

## Exclude variables

```{r}
config_$var_grouping = as.factor(config_$var_grouping)
levels(config_$var_grouping)

var_post = remove_na(config_$Column[ config_$var_period=='post' ])
var_hcp = config_$Column [ config_$var_grouping == "Physician Characteritics" ]
var_diff = config_$Column[ str_detect(config_$Column,'_diff') ]

length(var_post)
length(var_hcp)
length(var_diff)

var_diff

var2eliminate = var_diff
config_ = config_ %>% filter( !(Column %in% var2eliminate  )) 
combined_ = combined_ %>% select( -one_of(var2eliminate))

dim(combined_)
dim(config_) 

```

## Let's verify the data types

```{r}
class_type = as.data.frame( sapply(combined_, class))
is_integer =class_type == "integer"

key = which(config_$Type=="key")

selected_num = which(config_$Type=="numerical" & ! is_integer)
selected_int = which(config_$Type=="numerical" & is_integer)
selected_cat = which(config_$Type=="categorical")

selected_all = c(selected_cat, selected_int, selected_num)

var_stat = c(length(selected_cat), length(selected_num), length(selected_int))
var_stat
sum(var_stat)

```
## extreme values

```{r}
dim(config_[c(key,selected_num),])
dim(combined_  %>% select( one_of(config_$Column[c(key,selected_num)])))

write_csv(config_[c(key,selected_num),], 
  paste0(results_dir, 'modelling_var_config_num.csv'))

combined_num = extreme_values(
  combined_  %>% select( one_of(config_$Column[c(key,selected_num)])),
  var_config = paste0(results_dir, 'modelling_var_config_num.csv'),
  pth = 0.99)

combined_num = combined_num$data %>%   select( - one_of('pat_id'))
```

## Check the cat variables

```{r}
combined$tec_activation_group =str_replace(combined$tec_activation_group,'\\r','')
combined$tec_activation_group [ combined$tec_activation_group=="" ] = NA
combined$tec_activation_group = as.factor(combined$tec_activation_group)
levels(combined$tec_activation_group)

var_cat = which(config_$Type=='categorical')

```

## convert to dummy_vars for categorical variables
```{r}

write_csv(config_[c(key,selected_cat),],
  paste0(results_dir, "modelling_var_config_cat.csv"))

exclude_hcp = FALSE
if (! exclude_hcp) {
  mschool = factor2numeric(combined_$medical_school_desc)
  combined_$medical_school_desc = mschool$value
  saveRDS(mschool$map,'D:/Results/attributes/mschool_map.rds')
  
  specialty = factor2numeric(combined_$specialty)
  combined_$specialty = specialty$value
  saveRDS(specialty$map,'D:/Results/attributes/specialty_map.rds')
  
  specialty_cat = factor2numeric(combined_$specialty_cat)
  combined_$specialty_cat = specialty_cat$value
  saveRDS(specialty_cat$map,'D:/Results/attributes/specialty_cat_map.rds')
}

combined_cat = dummy_vars(combined_ %>% 
  select( one_of(config_$Column[c(key,selected_cat)])),
  var_config = paste0(results_dir, 'modelling_var_config_cat.csv'))

combined_cat = combined_cat$dummyfied %>%   select( - one_of('pat_id'))

combined_int = combined_ %>% select( one_of(config_$Column[c(selected_int)]))

#data_numeric <- as.data.frame(sapply(data, function(x) { as.numeric(as.character(x))}))

```

## run full xgboost

```{r}
data = cbind(combined_cat, combined_num, combined_int)
data$label = data$discontinue_flg_1_0
data$discontinue_flg_1_0 = NULL

data$label = as.factor(data$label)
table(data$label)

colnames_ = make_var_name(colnames(data))
colnames(data) = colnames_

dataset = makeClassifTask(id='full', data=data, target='label', positive=1)
lrn_xgb <- makeLearner(cl = "classif.xgboost", predict.type = "prob")

lrn_xgb$par.vals <- list(nrounds = 100,
                         verbose = TRUE,
                         objective = "binary:logistic")

# make resample object
rdesc <- makeResampleDesc(method = "CV", iters = 3)

# resample
res <- mlr::resample(learner = lrn_xgb, task = dataset, resampling = rdesc)

analyse_res_cv(res, results_dir = results_dir)

# train a single model
xgb_model <- train(learner = lrn_xgb, task = dataset)

write_xgb_model(xgb_model, results_dir = results_dir, dataset = dataset)


```

## 

```{r}
```