---
title: "Modelling with the agreed universe of features"
author: "Norman Poh"
date: "6 October 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Local set up

1. First, mount your data folder in Windows command prompt:
subst L: C:\Users\npoh\Documents\myProjects\Biogen_Tecfidera

2. set up local data drive
subst D: C:\Users\npoh\Documents\myProjects\Biogen_Tecfidera

```{r}
rm(list = ls())
setwd("L:/modelling")
library(palab)
library(palabmod)
library(ggplot2)
library(tidyverse)
library(stringr)
library(lubridate)
library(tictoc)
library(hashmap)
library(xgboost)
library(R.utils)
library(ROCR)
library(pROC) # to calculate auc
sourceDirectory("../lib")
source("../lib/analyse_res_cv.R")
source("../lib/write_xgb_model.R")
source("../lib/factor2numeric.R")
source("../lib/make_var_name.R")

```

```{r}

results_dir = "D:/Results/modelling_04_post_index_remove_top_var/"
mkdirs(results_dir)
```

## Load the original variables

```{r}
config = readRDS("D:/Data/Processed/combined_date_complied_config.rds")
combined = readRDS("D:/Data/Processed/combined_date_complied_data.rds")
```
## Correct variables

```{r}
#combined$tec_activation_group =str_replace(combined$tec_activation_group,'\\r','')
#combined$tec_activation_group [ combined$tec_activation_group=="" ] = NA
#combined$tec_activation_group = as.factor(combined$tec_activation_group)
#levels(combined$tec_activation_group)
```

## Correct the config file since we based our var-removal criteria based on these

```{r}
```
##  Eliminating variables

The universe of features consists of  "all counts + HCP + last date of date difference in the pre-index period except co-morbidities, and except post-index variables (which include tec_up, copay, etc)"

If we retain the "last date of date difference in the pre-index period", that means we eliminate the "first date difference variables in the pre-index period"

### Summary

I have worked out a list of variables to be eliminated on the basis of:
1.	100% missing
2.	Having only 1 unique value when it is a numerical variable 
3.	Having no value for the positive class
4.	Perfect separation on the basis of zero equal error rate; which indicates them being self-predictors. Three variables are: follow_up_end_dt_diff, disc_dt_diff, tot_dayssup_180)
5.	Very low equal error rate but nonzero, again, due to being a self-predictor, e.g., the total number of tecfidera fills (sum_fill)
6.	Having no more than 5 observed measurements for the positive class
7.	Having no more than 10 observed measurements for the positive class

In total, 123 variables are eliminated and so we have 321 usable variables in the end (plus 1 for pat_id)

### Further elimination based on the agreed universal feature

The implementation of this is based on:

1. All post-index var are to be removed
2. var with fst (First) in the pre-index period are to be removed (var with last date-diff at pre-index is hence retained)
3. Var with co-morbidities date difference are to be removed

This is in addition to:
* Variables of 'others' data type

So, we are left with 164 variables in the end -- see below

```{r}
eer_table = read_csv('D:/Data/QC/num_eer_analysis.csv')

# eliminate var that is empty
var2remove = c('pre_concom_gpif_fst8','pre_concom_gpif_lst8','pre_medication_fst11','pre_medication_lst11','pre_medication_fst13','pre_medication_lst13','pre_concom_gpif_fst8_diff','pre_concom_gpif_lst8_diff','pre_medication_fst11_diff','pre_medication_lst11_diff','pre_medication_fst13_diff','pre_medication_lst13_diff','pre_script_fst_diff','pre_script_lst_dayssup_diff','post_script_lst_dayssup_diff','pre_concom_gpif_num8','pre_medication_num11','pre_medication_num13','pre_concom_ndc_fst4_diff','pre_concom_ndc_lst4_diff')

# manually removed var
var2remove_manually = c('age_group','tec_up','copay_tecfidera','copay_avg_norm','post_script_lst_diff','post_script_lst_dayssup')

var2remove_manually_additional = 'post_lab_radio_date_fst_diff' #c('post_lab_radio_date_fst_diff','post_mgmt_date_fst_diff','post_other_outpat_date_fst_diff')



# var of others Type are to be removed
var_others = config$Column[config$Type=='others']
length(var_others)

# Elimination based on EER and number of positivie criteria
table.eliminate = eer_table %>% filter( (eer <0.04 |  `# pos`<=10 ) )
# should get 123 at this point
length(unique(  c(table.eliminate$Column, var2remove)))

# We will use post-index var
# var_post = config$Column[config$var_period=='post']

# var with fst (First) in the pre-index period are to be removed
var_fst_pre = config$Column [ str_detect(config$Column, 'fst') 
  & str_detect(config$Column, 'pre') ]

# var with lst (Last) in the pre-index period are to be removed? We just calculate them for now
var_lst_post = config$Column [ str_detect(config$Column, 'lst') 
  & str_detect(config$Column, 'post') ]

var_fst_post = config$Column [ str_detect(config$Column, 'fst') 
  & str_detect(config$Column, 'post') ]

#which of the variables in which we have last but not the first?
setdiff(str_replace(var_lst_post,'lst', ''), str_replace(var_fst_post,'fst', ''))

# var with co-morbidities date difference are to be removed
var_comdx_diff = config$Column [ config$var_grouping == "Co-morbidities - General" 
  & str_detect(config$Column, '_diff$')]

var2eliminate = unique(  c(table.eliminate$Column, var2remove, 
  var_others, var_fst_pre, var_lst_post, var_comdx_diff, var2remove_manually, var2remove_manually_additional) )

var_stat = c(length(var_fst_pre), 
  length(var_lst_post), length(var_comdx_diff), length(var2remove_manually))
var_stat
sum(var_stat)

length(var2eliminate)  
```

## remove the variables!


```{r}
config_ = config %>% filter( !(Column %in% var2eliminate  )) 
combined_ = combined %>% select( -one_of(var2eliminate))

length(config$Column)  
length(config_$Column) 

dim(combined_)
dim(config_) 

# save the variable list for audit purposes
config$isIncluded = config$Column %in% config_$Column
mkdirs('D:/Results/modelling_04_post_index_remove_top_var/Data')
write_csv(config, 'D:/Results/modelling_04_post_index_remove_top_var/Data/config_isIncluded.csv')

#for audit use and subsequent experiments
saveRDS(combined_, 'D:/Results/modelling_04_post_index_remove_top_var/Data/combined_.rds')

```

We are left with 203 variables in the end (including the key or pat_id)

## Divide data HCP, count, diff

```{r}
var_hcp = config_$Column [ config_$var_grouping == "Physician Characteritics" ]

#var_post = config_$Column [ config_$var_period == "post" ]

#diff variables excluding HCP
#var_diff_pre = config_$Column[ str_detect(config_$Column,'_diff') &  config_$var_period == "pre"]
#var_diff_post = config_$Column[ str_detect(config_$Column,'_diff') &  config_$var_period == "post"]
#var_num_post = config_$Column[ str_detect(config_$Column,'num') &  config_$var_period == "post"]
#var_diff_pre = setdiff(var_diff_pre, var_hcp)
#var_diff_post = setdiff(var_diff_post, var_hcp)

var_pre = config_$Column [config_$var_period == "pre"]
var_post = config_$Column [config_$var_period == "post"]

var_everything_else = setdiff(config_$Column, 
  union(union(var_hcp, var_pre), var_post))
  #union(union(union(var_hcp, var_diff_pre),var_diff_post), var_num_post))

config_$is_hcp= config_$Column %in% var_hcp
config_$is_pre= config_$Column %in% var_pre
config_$is_post= config_$Column %in% var_post
config_$is_everything_else = config_$Column %in% var_everything_else


var2use = vector('list',4)
var2use[[1]] = c(var_everything_else, var_pre)
var2use[[2]] = c(var_everything_else, var_pre, var_hcp)
var2use[[3]] = c(var_everything_else, var_pre, var_post)
var2use[[4]] = c(var_everything_else, var_pre, var_post, var_hcp)

cname =c('basic','basic_hcp','basic_post', 'basic_post_hcp' )

#for audit use
write_csv(config_, 'D:/Results/modelling_04_post_index_remove_top_var/Data/config_.csv')

```
## additional correction for the labelling; if we don't make these changes, mlr will complain!
```{r}
mschool = factor2numeric(combined$medical_school_desc)
combined$medical_school_desc = mschool$value

specialty = factor2numeric(combined$specialty)
combined$specialty = specialty$value

specialty_cat = factor2numeric(combined$specialty_cat)
combined$specialty_cat = specialty_cat$value

```

## Experiments

```{r}
for (i in 1:4) {
  
  results_dir_  = paste0('D:/Results/modelling_04_post_index_remove_top_var/xgb_complied_', cname[i],'/')
  mkdirs(results_dir_)
  
  config_ = config %>% filter( (Column %in% var2use[[i]]  )) 
  combined_ = combined %>% select( one_of(var2use[[i]]))
  dim(config_)
  dim(combined_)
  
  
  class_type = as.data.frame( sapply(combined_, class))
  is_integer =class_type == "integer"
  
  key = which(config_$Type=="key")
  
  selected_num = which(config_$Type=="numerical" & ! is_integer)
  selected_int = which(config_$Type=="numerical" & is_integer)
  selected_cat = which(config_$Type=="categorical")
  
  selected_all = c(selected_cat, selected_int, selected_num)

  var_stat = c(length(selected_cat), length(selected_num), length(selected_int))
  var_stat
  sum(var_stat)
  
  # extrem value
  write_csv(config_[c(key,selected_num),], 
    paste0(results_dir_, 'modelling_var_config_num.csv'))

  combined_num = extreme_values(
    combined_  %>% select( one_of(config_$Column[c(key,selected_num)])),
    var_config = paste0(results_dir_, 'modelling_var_config_num.csv'),
    pth = 0.99)

  combined_num = combined_num$data %>%   select( - one_of('pat_id'))

  #cat variable
  write_csv(config_[c(key,selected_cat),],
    paste0(results_dir_, "modelling_var_config_cat.csv"))


  combined_cat = dummy_vars(combined_ %>% 
    select( one_of(config_$Column[c(key,selected_cat)])),
    var_config = paste0(results_dir_, 'modelling_var_config_cat.csv'))
    
  combined_cat = combined_cat$dummyfied %>%   select( - one_of('pat_id'))
  
  #integer variable
  combined_int = combined_ %>% select( one_of(config_$Column[c(selected_int)]))
  
  #now we have: combined_num, combined_cat, combined_int, so we can run xgboost
  data = cbind(combined_cat, combined_num, combined_int)
  data$label = data$discontinue_flg_1_0
  data$discontinue_flg_1_0 = NULL
  
  data$label = as.factor(data$label)
  table(data$label)
  
  colnames_ = make_var_name(colnames(data))
  colnames(data) = colnames_
  
  dataset = makeClassifTask(id='full', data=data, target='label', positive=1)
  lrn_xgb <- makeLearner(cl = "classif.xgboost", predict.type = "prob")
  
  lrn_xgb$par.vals <- list(nrounds = 100, verbose = FALSE, objective = "binary:logistic")
  
  # make resample object
  rdesc <- makeResampleDesc(method = "CV", iters = 5, stratify=TRUE)
  
  # resample
  res <- mlr::resample(learner = lrn_xgb, task = dataset, resampling = rdesc)
  
  analyse_res_cv(res, results_dir = results_dir_)
  
  # train a single model
  xgb_model <- train(learner = lrn_xgb, task = dataset)
  
  write_xgb_model(xgb_model, results_dir = results_dir_, dataset = dataset)

}

```
