---
title: "Modelling with the agreed universe of features"
author: "Norman Poh"
date: "6 October 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Local set up

1. First, mount your data folder in Windows command prompt:
subst L: C:\Users\npoh\Documents\myProjects\Biogen_Tecfidera

2. set up local data drive
subst D: C:\Users\npoh\Documents\myProjects\Biogen_Tecfidera

```{r}
#rm(list = ls())
setwd("L:/modelling")
library(palab)
library(palabmod)
library(ggplot2)
library(tidyverse)
library(stringr)
library(lubridate)
library(tictoc)
library(hashmap)
library(xgboost)
library(R.utils)
library(ROCR)
library(pROC) # to calculate auc

source("L:/Lib/analyse_res_cv.R")
source("L:/Lib/calculate_eer.R")
source("L:/Lib/config_with_colnames.R")
source("L:/Lib/create_date_diffs.R")
source("L:/Lib/cut_linux.R")
source("L:/Lib/factor2numeric.R")
source("L:/Lib/make_negative.R")
source("L:/Lib/make_positive.R")
source("L:/Lib/make_var_name.R")
source("L:/Lib/mystat.R")
source("L:/Lib/plot_cond_density.R")
source("L:/Lib/remove_inf.R")
source("L:/Lib/remove_na.R")
source("L:/Lib/write_xgb_model.R")

```

```{r}

results_dir = "D:/Results/modelling_05_clinical_specific/"
mkdirs(results_dir)
```

## Load the original variables

```{r}
config = readRDS("D:/Data/Processed/combined_date_complied_config.rds")
combined = readRDS("D:/Data/Processed/combined_date_complied_data.rds")

```

## add new data -- does nothing for the moment.
```{r}
raw = read_csv("D:/Data/Flat_File_v6/mapped_id.csv",
               col_types = (cols(pat_id = col_character(), .default = col_guess())))
idmap = hashmap(raw$pat_id, raw$mapped_id)

raw = read_csv("D:/Data/Flat_File_v7/BGN_1158015_pat_data.csv",
               col_types = (cols(pat_id = col_character(), .default = col_guess())))
```
## Correct variables

```{r}


```

## Correct the config file since we based our var-removal criteria based on these

```{r}
```
##  Eliminating variables

The universe of features consists of  "all counts + HCP + last date of date difference in the pre-index period except co-morbidities, and except post-index variables (which include tec_up, copay, etc)"

If we retain the "last date of date difference in the pre-index period", that means we eliminate the "first date difference variables in the pre-index period"

### Summary

I have worked out a list of variables to be eliminated on the basis of:
1.	100% missing
2.	Having only 1 unique value when it is a numerical variable 
3.	Having no value for the positive class
4.	Perfect separation on the basis of zero equal error rate; which indicates them being self-predictors. Three variables are: follow_up_end_dt_diff, disc_dt_diff, tot_dayssup_180)
5.	Very low equal error rate but nonzero, again, due to being a self-predictor, e.g., the total number of tecfidera fills (sum_fill)
6.	Having no more than 5 observed measurements for the positive class
7.	Having no more than 10 observed measurements for the positive class

In total, 123 variables are eliminated and so we have 321 usable variables in the end (plus 1 for pat_id)

### Further elimination based on the agreed universal feature

The implementation of this is based on:

1. All post-index var are to be removed
2. var with fst (First) in the pre-index period are to be removed (var with last date-diff at pre-index is hence retained)
3. Var with co-morbidities date difference are to be removed

This is in addition to:
* Variables of 'others' data type

So, we are left with 164 variables in the end -- see below

```{r}
#------------------------------------------------------------------------------------------------
# eliminate var that is empty
var2remove = c('pre_concom_gpif_fst8','pre_concom_gpif_lst8','pre_medication_fst11','pre_medication_lst11','pre_medication_fst13','pre_medication_lst13','pre_concom_gpif_fst8_diff','pre_concom_gpif_lst8_diff','pre_medication_fst11_diff','pre_medication_lst11_diff','pre_medication_fst13_diff','pre_medication_lst13_diff','pre_script_fst_diff','pre_script_lst_dayssup_diff','post_script_lst_dayssup_diff','pre_concom_gpif_num8','pre_medication_num11','pre_medication_num13','pre_concom_ndc_fst4_diff','pre_concom_ndc_lst4_diff')

# Elimination based on EER and number of positivie criteria
eer_table = read_csv('D:/Data/QC/num_eer_analysis.csv')
table.eliminate = eer_table %>% filter( (eer <0.04 |  `# pos`<=10 ) )

#------------------------------------------------------------------------------------------------
# manually removed var - agre_group due to duplicate;
# remove copay_tecfidera because it is calculated on the toality of 180 days post-index
var2remove_manually = c('age_group', 'copay_tecfidera')

# we now get 125 instead of 123
var2remove_ = unique(  c(table.eliminate$Column, var2remove,var2remove_manually))
length(var2remove_)


#------------------------------------------------------------------------------------------------
# var of others Type are to be removed
configFiltered = config %>% filter( Type != 'others') %>% 
  filter (! (Column %in% var2remove_))
dim(configFiltered) # we now have 318 variables


#------------------------------------------------------------------------------------------------
#resource utilisation

#------------------------------------------------------------------------------------------------
#resource utilisation
var_post_resource = configFiltered$Column[ configFiltered$var_period == 'post' 
  & configFiltered$var_grouping == 'Resource Utilization']
#It has diff and count; and we remove the count of resources because it is calculated on post-index 180 days as opposed to from index date to discontinuation date, so they are potentially not generalisable

var_post_resource_diff = var_post_resource [ str_detect(var_post_resource, '_diff') ] 
var_post_resource_count = setdiff(var_post_resource, var_post_resource_diff)

var_post_resource_diff  # we want to keep them - to be used in model 3; this includes post_script_lst_diff, which was discussed

var_post_resource_diff_fst = var_post_resource_diff[ str_detect(var_post_resource_diff,'fst')]
var_post_resource_diff_lst = setdiff(var_post_resource_diff, var_post_resource_diff_fst)

var_post_resource_count # we will remove this; this includes post_script_lst_dayssup which we discussed

#remove var_post_resource_count and last occurence post-index resource vars here definitely
configFiltered = configFiltered %>% filter (! (Column %in% 
  c(var_post_resource_count,var_post_resource_diff_lst) ) )
dim(configFiltered) # we now have 305 variables

#------------------------------------------------------------------------------------------------
# Treatment pattern
#we remove them but may put them back later
var_post_treatment = configFiltered$Column[ configFiltered$var_period == 'post' 
  & configFiltered$var_grouping == 'Treatment Patterns']

#there is only tec_up here!

#------------------------------------------------------------------------------------------------
# financial burden
var_post_finburden = configFiltered$Column[ configFiltered$var_period == 'post' 
  & configFiltered$var_grouping == 'Financial Burden']

var_post_finburden

#we had -- "copay_tecfidera" "copay_avg_norm" but now copay_avg_norm only

#------------------------------------------------------------------------------------------------
# pre-index but need to exclude last date
var_pre = configFiltered$Column[ configFiltered$var_period == 'pre']
var_pre_last = var_pre [ str_detect(var_pre, 'lst') ] # to delete them
var_pre_first = setdiff(var_pre, var_pre_last)

#Remove the var_pre_first
configFiltered = configFiltered %>% filter ( !(Column %in% var_pre_first ) ) 
dim(configFiltered) # we now have 305 variables

#------------------------------------------------------------------------------------------------
# post-index of everything except financial burden and treatment and resources
var_post = configFiltered$Column[ configFiltered$var_period == 'post' ]

var_post = setdiff( var_post,
                    c(var_post_finburden, var_post_treatment, 
                      var_post_resource_diff_fst))
var_post
#------------------------------------------------------------------------------------------------
# Check the variable left over
var_post_fst = configFiltered$Column[ str_detect(configFiltered$Column, 'post') & 
  str_detect(configFiltered$Column, 'fst')]
var_post_lst = configFiltered$Column[ str_detect(configFiltered$Column, 'post') & 
  str_detect(configFiltered$Column, 'lst')]

configFiltered =configFiltered %>% filter( !(Column %in% var_post_fst))

var_so_far = unique(c(var_pre_last, var_post_finburden, var_post_treatment,
  var_post_resource_diff_fst, var_post_lst ))

var_left_over = setdiff(configFiltered$Column,var_so_far)
var_left_over

View(configFiltered %>% filter( Column %in% var_left_over))
  #configFiltered$Column[ configFiltered$var_period == 'post' ]

check_ = configFiltered %>% filter( Column %in% var_left_over)
check_ = as.data.frame(table(check_$var_grouping))
# We will use post-index var
# var_post = config$Column[config$var_period=='post']

var_to_remove = setdiff(config$Column, 
  union_all(var_left_over, var_pre_last, var_post_lst, var_post_resource_diff_fst,
            var_post_treatment, var_post_finburden))
```
## var to remove
```{r}
#------------------------------------------------------------------------------------------------
# Check the variable left over

config$v1 = config$Column %in% union(var_left_over, var_pre_last) # var used for model 1
config$v2 = config$Column %in% var_post_fst # var used for model 2 and so on
config$v3 = config$Column %in% var_post_resource_diff_fst
config$v4 = config$Column %in% c(var_post_treatment, var_post_finburden)

config__ = config %>% select( one_of(paste0('v',0:4)) )
stat_ = as.data.frame(sapply(config__,sum))
colnames(stat_) <- 'sum'
stat_
sum(stat_)
dim(config)
write_csv(config, paste0(results_dir, 'annotated_var_config.csv'))
```

## remove the variables!


```{r}
config = read_csv('D:/Results/modelling_05_clinical_specific/annotated_var_config_verified.csv')

config$v0  = !(config$v1 | config$v2 | config$v3 | config$v4)

# checking
config__ = config %>% select( one_of(paste0('v',0:4)) )
stat_ = as.data.frame(sapply(config__,sum))
colnames(stat_) <- 'sum'
stat_
sum(stat_)

#write_csv(config, 'D:/Results/modelling_05_clinical_specific/annotated_var_config_verified.csv')

var2eliminate = config$Column[  config$v0 ]
config_ = config %>% filter( !(Column %in% var2eliminate ) )
combined_ = combined %>% select( -one_of(var2eliminate))

length(config_$Column) 



dim(combined_)
dim(config_) 

```

## Divide data HCP, count, diff

```{r}
var2use = vector('list',4)
var2use[[1]] = config_$Column [ config_$v1]
var2use[[2]] = config_$Column [ config_$v1 | config_$v2]
var2use[[3]] = config_$Column [ config_$v1 | config_$v2 | config_$v3]
var2use[[4]] = config_$Column [ config_$v1 | config_$v2 | config_$v3 | config_$v4 ]
var2use[[5]] = config_$Column [ config_$v3 ] # resource only

cname = paste0('v',1:5)

for (i in 1:5) {
  print( length(var2use[[i]]) )
}
```
## additional correction for the labelling; if we don't make these changes, mlr will complain!
```{r}

mschool = factor2numeric(combined$medical_school_desc)
combined$medical_school_desc = mschool$value
mschool_table = tibble(key = mschool$map$keys() , value = mschool$map[[ mschool$map$keys() ]])
write_csv(mschool_table, "D:/Results/attributes/medical_school_desc.csv")

specialty = factor2numeric(combined$specialty)
combined$specialty = specialty$value
specialty_table = tibble(key = specialty$map$keys() , value = specialty$map[[ specialty$map$keys() ]])
write_csv(specialty_table, "D:/Results/attributes/specialty.csv")

specialty_cat = factor2numeric(combined$specialty_cat)
combined$specialty_cat = specialty_cat$value
specialty_cat_table = tibble(key = specialty_cat$map$keys() , value = specialty_cat$map[[ specialty_cat$map$keys() ]])
write_csv(specialty_cat_table, "D:/Results/attributes/specialty_cat.csv")

```

## Experiments

```{r}

for (i in 1:5) {
  
  results_dir_  = paste0(results_dir,'xgb_', cname[i],'/')
  mkdirs(results_dir_)
  
  config_ = config %>% filter( (Column %in% 
    union_all('discontinue_flg','pat_id',var2use[[i]])  )) 
  combined_ = combined %>% select( one_of(
    union_all('discontinue_flg','pat_id',var2use[[i]])))
  dim(config_)
  dim(combined_)
  
  key = which(config_$Column=='pat_id')
  
  class_type = as.data.frame( sapply(combined_, class))
  is_integer =class_type == "integer"
  
  selected_num = which(config_$Type=="numerical" & ! is_integer)
  selected_int = which(config_$Type=="numerical" & is_integer)
  selected_cat = which(config_$Type=="categorical")
  
  selected_all = c(selected_cat, selected_int, selected_num)

  var_stat = c(length(selected_cat), length(selected_num), length(selected_int))
  var_stat
  sum(var_stat)
  
  # extrem value
  if (length(selected_num)>0) {
    write_csv(config_[c(key,selected_num),], 
      paste0(results_dir_, 'modelling_var_config_num.csv'))
    combined_num = extreme_values(
        combined_  %>% select( one_of(config_$Column[c(key,selected_num)])),
        var_config = paste0(results_dir_, 'modelling_var_config_num.csv'),
        pth = 0.99,
        output_dir = results_dir_)
    combined_num = combined_num$data %>%   select( - one_of('pat_id'))
  } else {
    combined_num=combined_ %>% select( one_of('dodo'))
  }
  
  
  #cat variable
  if (length(selected_cat)>0) {
    write_csv(config_[c(key,selected_cat),],
      paste0(results_dir_, "modelling_var_config_cat.csv"))
  
    combined_cat = dummy_vars(combined_ %>% 
      select( one_of(config_$Column[c(key,selected_cat)])),
      var_config = paste0(results_dir_, 'modelling_var_config_cat.csv'),
      output_dir = results_dir_)
      
    combined_cat = combined_cat$dummyfied %>%   select( - one_of('pat_id'))
  } else {
    combined_cat=combined_ %>% select( one_of('dodo'))
  }
  
  #integer variable
  combined_int = combined_ %>% select( one_of(config_$Column[c(selected_int)]))
  
  #now we have: combined_num, combined_cat, combined_int, so we can run xgboost
  data = cbind(combined_cat, combined_num, combined_int)
  data$label = data$discontinue_flg_1_0
  data$discontinue_flg_1_0 = NULL
  
  data$label = as.factor(data$label)
  table(data$label)
  
  colnames_ = make_var_name(colnames(data))
  colnames(data) = colnames_
  
  dataset = makeClassifTask(id='full', data=data, target='label', positive=1)
  lrn_xgb <- makeLearner(cl = "classif.xgboost", predict.type = "prob")
  
  lrn_xgb$par.vals <- list(nrounds = 100, verbose = FALSE, objective = "binary:logistic")
  
  # make resample object
  rdesc <- makeResampleDesc(method = "CV", iters = 5, stratify=TRUE)
  
  # resample
  res <- mlr::resample(learner = lrn_xgb, task = dataset, resampling = rdesc)
  
  analyse_res_cv(res, results_dir = results_dir_)
  
  # train a single model
  xgb_model <- train(learner = lrn_xgb, task = dataset)
  
  write_xgb_model(xgb_model, results_dir = results_dir_, dataset = dataset)

}

```
## Load the spreadsheet
```{r}

fnames = vector('list',5)
for (i in 1:5) {
  fnames[[i]]  = paste0(results_dir,'xgb_',
    cname[i],'/PRCurve_XGB_3fold_freq_100_bins.csv')
}

prec = vector('list',5)
for (i in 1:5) {
  prec[[i]] = read_csv(fnames[[i]])
}

table_ = tibble( prec[[1]]$rec_binned[1:100], prec[[1]]$prec[1:100], 
  prec[[2]]$prec[1:100], prec[[3]]$prec[1:100], prec[[4]]$prec[1:100], prec[[5]]$prec[1:100])
colnames(table_) = c('Recall bin', cname)

write_csv(table_, paste0(results_dir,'PR_curves.csv'))
```

## print var importance

```{r}
Description = hashmap(config$Column, config$Description)

vi_fnames = vector('list',5)
for (i in 1:5) {
  vi_fnames[[i]]  = paste0(results_dir,
    'xgb_',cname[i],
    '/VI_XGB_freq_singlemodel.csv')
}

# add the description back
vi = vector('list',5)
for (i in 1:5) {
  vi[[i]] = read_csv(vi_fnames[[i]])
  vi[[i]]$Description = Description [[vi[[i]]$Feature]]
  fname = paste0(results_dir,
    'xgb_',cname[i],
    '/VI_XGB_freq_singlemodel_Decription.csv')
  write_csv(vi[[i]], fname)
}



```
## get the stat

```{r}
bivar = read_csv('D:/Data/QC/bivar_stats_num/bivar_stats_y_flag.csv')
vi_ = read_csv('D:/Results/modelling_05_clinical_specific/xgb_v2/VI_XGB_freq_singlemodel_Decription.csv')
corr_map = hashmap(bivar$Variable, bivar$Correlation)
eer_map = hashmap(eer_table$Column, eer_table$eer)

var_grouping = hashmap(config$Column, config$var_grouping)

# top ten
n_=40
table_ = tibble(Column =vi_$Feature[1:n_], 
  Corr= corr_map[[ vi_$Feature[1:n_] ]],
  eer = eer_map[[ vi_$Feature[1:n_] ]],
  Description = Description[[ vi_$Feature[1:n_] ]],
  var_grouping = var_grouping[[ vi_$Feature[1:n_] ]]
  )


write_csv(table_, 'D:/Results/modelling_05_clinical_specific/model2_top40_stat.csv')

table(var_grouping[[ vi_$Feature[1:30] ]])
```

## do propoer training and testing --> go to 08_*.Rmd

```{r}


```

## STOP HERE













## Model two patient profile

```{r}
res = readRDS('D:/Results/modelling_05_clinical_specific/xgb_v2/res_XGB_3fold.rds')
res = res$pred$data
pred_order <- BBmisc::sortByCol(res, col = "prob.1", asc = FALSE)

top_10 <- pred_order[1:10,]
top_10$pat_id = top_10$id
top_10$id <- NULL

#res$PATIENT_ID <- PATIENT_ID

top_10_patients <- left_join(top_10, combined, by = "pat_id")

# they are not aligned!!
top_10_patients$truth == top_10_patients$discontinue_flg


res = res %>% dplyr::rename(pat_id =id)

combined_ = plyr::join(combined, res)


order = sort(combined_$prob.1, index.return=TRUE, decreasing=TRUE)


selected =order$ix[1:10]
combined_$prob.1[selected]

table_ = as.data.frame(t(combined_[selected,]))
View(table_)

combined__ = combined_[selected,]
write_csv(combined__,
  'D:/Results/modelling_05_clinical_specific/top_10_pat_model2_combined.csv')

combined_$discontinue_flg == combined_$truth

View(combined_[order$ix[1:100],c('pat_id','prob.1','truth')])
max(res$pred$data$prob.1)


```