---
title: "Modelling with the agreed universe of features"
author: "Norman Poh"
date: "6 October 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Local set up

1. First, mount your data folder in Windows command prompt:
subst L: C:\Users\npoh\Documents\myProjects\Biogen_Tecfidera

2. set up local data drive
subst D: C:\Users\npoh\Documents\myProjects\Biogen_Tecfidera

```{r}
rm(list = ls())
setwd("L:/modelling")
library(palab)
library(palabmod)
library(ggplot2)
library(tidyverse)
library(stringr)
library(lubridate)
library(tictoc)
library(hashmap)
library(xgboost)
library(R.utils)
library(ROCR)
library(pROC) # to calculate auc

source("L:/Lib/analyse_res_cv.R")
source("L:/Lib/calculate_eer.R")
source("L:/Lib/config_with_colnames.R")
source("L:/Lib/create_date_diffs.R")
source("L:/Lib/cut_linux.R")
source("L:/Lib/factor2numeric.R")
source("L:/Lib/make_negative.R")
source("L:/Lib/make_positive.R")
source("L:/Lib/make_var_name.R")
source("L:/Lib/mystat.R")
source("L:/Lib/plot_cond_density.R")
source("L:/Lib/remove_inf.R")
source("L:/Lib/remove_na.R")
source("L:/Lib/write_xgb_model.R")

```

```{r}

results_dir = "D:/Results/modelling_05_clinical_specific/"
mkdirs(results_dir)
```

## Load the original variables

```{r}
#config = readRDS("D:/Data/Processed/combined_date_complied_config.rds")
config = read_csv('D:/Results/modelling_05_clinical_specific/annotated_var_config_verified.csv')

combined = readRDS("D:/Data/Processed/combined_date_complied_data.rds")

```

## add new data -- does nothing for the moment.
```{r}
#raw = read_csv("D:/Data/Flat_File_v6/mapped_id.csv",
#               col_types = (cols(pat_id = col_character(), .default = col_guess())))
#idmap = hashmap(raw$pat_id, raw$mapped_id)
#
#raw = read_csv("D:/Data/Flat_File_v7/BGN_1158015_pat_data.csv",
#               col_types = (cols(pat_id = col_character(), .default = col_guess())))
```
## Get the map up

```{r}
Description = hashmap(config$Column, config$Description)
var_grouping = hashmap(config$Column, config$var_grouping)
var_period = hashmap(config$Column, config$var_period)
```

## remove the variables!

```{r}
config$v0  = !(config$v1 | config$v2 | config$v3 | config$v4)

# checking
config__ = config %>% select( one_of(paste0('v',0:4)) )
stat_ = as.data.frame(sapply(config__,sum))
colnames(stat_) <- 'sum'
stat_
sum(stat_)

#write_csv(config, 'D:/Results/modelling_05_clinical_specific/annotated_var_config_verified.csv')

var2eliminate = config$Column[  config$v0 ]
config_ = config %>% filter( !(Column %in% var2eliminate ) )
combined_ = combined %>% select( -one_of(var2eliminate))

length(config_$Column) 



dim(combined_)
dim(config_) 

```

## Divide data HCP, count, diff

```{r}
var2use = vector('list',4)
var2use[[1]] = config_$Column [ config_$v1]
var2use[[2]] = config_$Column [ config_$v1 | config_$v2]
var2use[[3]] = config_$Column [ config_$v1 | config_$v2 | config_$v3]
var2use[[4]] = config_$Column [ config_$v1 | config_$v2 | config_$v3 | config_$v4 ]
var2use[[5]] = config_$Column [ config_$v3 ] # resource only

cname = paste0('v',1:5)

for (i in 1:5) {
  print( length(var2use[[i]]) )
}
```
## additional correction for the labelling; if we don't make these changes, mlr will complain!
```{r}

mschool = factor2numeric(combined$medical_school_desc)
combined$medical_school_desc = mschool$value
mschool_table = tibble(key = mschool$map$keys() , value = mschool$map[[ mschool$map$keys() ]])
write_csv(mschool_table, "D:/Results/attributes/medical_school_desc.csv")

specialty = factor2numeric(combined$specialty)
combined$specialty = specialty$value
specialty_table = tibble(key = specialty$map$keys() , value = specialty$map[[ specialty$map$keys() ]])
write_csv(specialty_table, "D:/Results/attributes/specialty.csv")

specialty_cat = factor2numeric(combined$specialty_cat)
combined$specialty_cat = specialty_cat$value
specialty_cat_table = tibble(key = specialty_cat$map$keys() , value = specialty_cat$map[[ specialty_cat$map$keys() ]])
write_csv(specialty_cat_table, "D:/Results/attributes/specialty_cat.csv")

```

## Experiments

```{r}

for (i in 2) {
  
  results_dir_  = paste0(results_dir,'xgb_profile_', cname[i],'/')
  mkdirs(results_dir_)
  
  config_ = config %>% filter( (Column %in% 
    union_all('discontinue_flg','pat_id',var2use[[i]])  )) 
  combined_ = combined %>% select( one_of(
    union_all('discontinue_flg','pat_id',var2use[[i]])))
  dim(config_)
  dim(combined_)
  
  key = which(config_$Column=='pat_id')
  
  class_type = as.data.frame( sapply(combined_, class))
  is_integer =class_type == "integer"
  
  selected_num = which(config_$Type=="numerical" & ! is_integer)
  selected_int = which(config_$Type=="numerical" & is_integer)
  selected_cat = which(config_$Type=="categorical")
  
  selected_all = c(selected_cat, selected_int, selected_num)

  var_stat = c(length(selected_cat), length(selected_num), length(selected_int))
  var_stat
  sum(var_stat)
  
  # extrem value
  if (length(selected_num)>0) {
    write_csv(config_[c(key,selected_num),], 
      paste0(results_dir_, 'modelling_var_config_num.csv'))
    combined_num = extreme_values(
        combined_  %>% select( one_of(config_$Column[c(key,selected_num)])),
        var_config = paste0(results_dir_, 'modelling_var_config_num.csv'),
        pth = 0.99,
        output_dir = results_dir_)
    combined_num = combined_num$data %>%   select( - one_of('pat_id'))
  } else {
    combined_num=combined_ %>% select( one_of('dodo'))
  }
  
  
  #cat variable
  if (length(selected_cat)>0) {
    write_csv(config_[c(key,selected_cat),],
      paste0(results_dir_, "modelling_var_config_cat.csv"))
  
    combined_cat = dummy_vars(combined_ %>% 
      select( one_of(config_$Column[c(key,selected_cat)])),
      var_config = paste0(results_dir_, 'modelling_var_config_cat.csv'),
      output_dir = results_dir_)
      
    combined_cat = combined_cat$dummyfied %>%   select( - one_of('pat_id'))
  } else {
    combined_cat=combined_ %>% select( one_of('dodo'))
  }
  
  #integer variable
  combined_int = combined_ %>% select( one_of(config_$Column[c(selected_int)]))
  
  #now we have: combined_num, combined_cat, combined_int, so we can run xgboost
  data = cbind(combined_cat, combined_num, combined_int)
  data$label = data$discontinue_flg_1_0
  data$discontinue_flg_1_0 = NULL
  
  data$label = as.factor(data$label)
  table(data$label)
  
  colnames_ = make_var_name(colnames(data))
  colnames(data) = colnames_
  
  #divide into training and testing
  k = dismo::kfold(data, 5, by=data$label)
  k_train = which(k<=4)
  k_test = which(k==5)
  
  #dataset = makeClassifTask(id='full', data=data[k_train,], target='label', positive=1)
  #dataset_test = makeClassifTask(id='full', data=data[k_test,], target='label', positive=1)
  dataset = makeClassifTask(id='full', data=data, target='label', positive=1)
  
  lrn_xgb <- makeLearner(cl = "classif.xgboost", predict.type = "prob")
  lrn_xgb$par.vals <- list(nrounds = 100, verbose = FALSE, objective = "binary:logistic")
  trained_model <- train(lrn_xgb, dataset)
  
  write_xgb_model(trained_model, results_dir = results_dir_, dataset = dataset)
  
  #pred <- predict(trained_model, dataset_test)
  pred <- predict(trained_model, dataset)
    
  #add the pat_id back
  #pred$data$pat_id = combined$pat_id[k_test]
  pred$data$pat_id = combined$pat_id
  
  dim(pred$data)
  length(k_test)
  #lrn_xgb$par.vals <- list(nrounds = 100, verbose = FALSE, objective = "binary:logistic")
  
  
  #get the order by prob.1
  order = sort(pred$data$prob.1, index.return=TRUE, decreasing=TRUE)
  
  #checking
  top_n = 20
  pred$data$prob.1[ order$ix[1:top_n] ]
  
  
  #re-order it
  pred_reordered = pred$data[order$ix,]
  
  top_20_patients <- left_join(pred_reordered[1:top_n,], combined_) #, by = "pat_id")
  
  # they are not aligned!!
  top_20_patients$truth == top_20_patients$discontinue_flg

  #transpose it
  table_ = as.data.frame(t(top_20_patients))
  table_$Column = rownames(table_)
  table_$Description = Description[[table_$Column]]
  table_$var_grouping = var_grouping[[table_$Column]]
  table_$var_period = var_period[[table_$Column]]
  
  table_ = table_ %>% select('Column','Description', 'var_grouping','var_period', everything())
  
  write_csv(table_,
    paste0(results_dir_,'top_20_pat_model2_combined_transposed_edited.csv'))

  #
  flag_is_na = table_$V1 == '0' |  is.na(table_$V1) 
  mytable = as.data.frame(table(table_$var_grouping, flag_is_na))
  write_csv(mytable,
     paste0(results_dir_,'top_20_pat_model2_combined_transposed_edited_p1.csv'))       
  #write_csv(top_20_patients,
  #  paste0(results_dir_,'top_20_pat_model2_combined.csv'))
  
  #write.table(table_,
  #  paste0(results_dir_,'top_20_pat_model2_combined_transposed.csv'),
  #  row.names = TRUE,  sep = ",")
  
  #load the file
  #table_ = read_csv(paste0(results_dir_,'top_20_pat_model2_combined_transposed.csv'))
  
   #write.table(table_,
   #  paste0(results_dir_,'top_20_pat_model2_combined_transposed_edited.csv'),
   #  row.names = TRUE,  sep = ",")
}

```
